A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$ methods

### 2024-11-07 paper_v01/article.tex
P_DCCA function explained

The $DMC_x^2$ function runs the $\rho_{DCCA}$ with \verb"P_DCCA_output_matrix" set to \verb"True".

>>>>

The $DMC_x^2$ function runs the $\rho_{DCCA}$ with \verb"P_DCCA_output_matrix" set to \verb"True". There is no \verb"DCCA_of" input for the $DMC_x^2$ function, instead there is a \verb"dmcx2_of" parameter. This input receives a 2D matrix where each line represents the indexes of the series to be used in Equation \ref{eq:dmcx2}. The first value of each row is the index of the serie used as the dependent variable, the others, the independent ones. There are two literal strings that can be used, for convenience as inputs for this parameter: \verb"'all-full'", that generates a 2D array with every series as the dependent variable against all the others; and \verb"'first-full'", with only one row, having the index zero series as the dependente variable in relation with all the others.
